---
title: "Midterm Project"
author: "Dan Barrett"
date: "10/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Part 1: Data Wranggling 

```{r}
library(tidyverse)
library(dplyr)
df = read_csv('midterm.csv')
```


```{r}
colSums(is.na(df))
df = subset(df, select = -c(payfix, admtype, asource, preopday, bwght, ecodub92, pt_state, diag_adm, er_mode, obs_hour, nicu_day))
```

Variable moa signals the month of admission & mod is the variable for month of discharge.

```{r}
df %>% count(moa)
df %>% filter(sex == 1) %>% count(moa)
df %>% filter((sex == 2) & (age >= 10) & (age <= 19)) %>% count(moa)
df %>% filter((moa == 10) & (sex == 2)) %>% count(provider)
```

- October has the highest number of admissions with 11,408
- October also had the highest number of male admissions with 5,164
- May the highest number of teenage female patients with 270 admissions
- Rhode Island Hospital (7205) had the most female patients in October with 1,517 female admissions

```{r}
df %>%group_by(sex) %>% summarise(mean = mean(age))
df %>% group_by(moa) %>% summarise(mean = mean(age))
df %>% group_by(provider) %>% summarise(mean = mean(tot))
df %>% filter((sex == 1) & (age >= 10) & (age <= 19)) %>% group_by(provider) %>% summarise(mean = mean(tot))
df %>% group_by(raceethn) %>% summarise(mean = mean(los))
```

- Female patients have a lower average age of 50.86 compared to the average age of male patients of 51.5
- January had the oldest average patient admitted, the patients that month had an average age of 51.79
- Bradley (7215) had the highest average total charge of $69,945.55
- Rodger Williams (7206) had the lowest average charge for teenage male patients ($10,360.44)
- Patients with the race American Indian had the longest average stay of 5.54 days compared to patients of other known races

```{r}
price <- df %>% filter((sex == 1) & (age == 20)) %>% summarise(mean = mean(tot))
stay <- df %>% filter((sex == 1) & (age == 20)) %>% summarise(mean = mean(los))
price / stay
```

-The average cost per day for a 20-year old male is $5,430.09 



## Part 3: Predictive Modeling 
```{r}
library(caret)
library(rattle)
library(rpart)
set.seed(2020)
```

```{r}
df <- read_csv('midterm.csv')
mysample <- df[sample(1:nrow(df), 2000,
   replace=FALSE),]
median_tot <- df %>% summarise(median = median(tot))
mysample$target <- case_when(
  mysample$tot <= 21854 ~ "low",
  TRUE ~ "high"
)
df = subset(mysample, select = c(age, sex, raceethn, provider, moa, mod, admtype, campus, los, target))
df$target <- factor(df$target)
df$sex <- factor(df$sex)
df$raceethn <- factor(df$raceethn)
df$provider <- factor(df$provider)
df$admtype <- factor(df$admtype)
df$campus <- factor(df$campus)
df <- df %>% na.omit((df$raceethn) | (df$admtype))
```



```{r}
splitIndex <- createDataPartition(df$target, p = .90, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
tree1 <- rpart(target ~ ., data = df_train, control=rpart.control(maxdepth= 3))
barplot(tree1$variable.importance)
fancyRpartPlot(tree1)
```




```{r}
tuneGrid = expand.grid(maxdepth = 1:10)
trControl = trainControl(method ="cv",number =5)
tree_approach1 <- train(target~., data=df_train ,method ="rpart2",trControl =trControl, tuneGrid = tuneGrid)
plot(tree_approach1)
```



```{r}
tuneGrid = expand.grid(nIter =2:10, method='cv')
trControl = trainControl(method ="cv",number =5)
tree_approach2 <- train(target~., data=df_train ,method ="adaboost",trControl =trControl, tuneGrid = tuneGrid)
plot(tree_approach2)
```



```{r}
tuneGrid = expand.grid(mtry = 2:5)
trControl = trainControl(method ="cv",number =5)
tree_approach3 <- train(target~., data=df_train ,method ="rf",trControl =trControl, tuneGrid = tuneGrid)
plot(tree_approach3)
```

```{r}
model_accuracy <- resamples(list(adaboost = tree_approach2,
                                 forest = tree_approach3,
                                 tree = tree_approach1))
```



```{r}
library(e1071)
tree_model <- rpart(target ~ ., data = df_train, control = rpart.control(maxdepth = 5))
pred <- predict(tree_approach1, df_test, type = "raw")
cm <- confusionMatrix(data = pred, reference = df_test$target, positive = "high")
cm$overall[1]
```



## Lenght of Stay Model Prediction
```{r}
df <- read_csv('midterm.csv')
median_tot <- df %>% summarise(median = median(tot))
df$target <- case_when(
  df$los <= 4 ~ "short",
  TRUE ~ "long"
)
df = subset(df, select = c(age, sex, raceethn, provider, moa, mod, admtype, campus, tot, target))
df$target <- factor(df$target)
df$sex <- factor(df$sex)
df$raceethn <- factor(df$raceethn)
df$provider <- factor(df$provider)
df$admtype <- factor(df$admtype)
df$campus <- factor(df$campus)
df <- df %>% na.omit((df$raceethn) | (df$admtype))
```


```{r}
splitIndex <- createDataPartition(df$target, p = .90, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
tuneGrid = expand.grid(maxdepth = 1:10)
trControl = trainControl(method ="cv",number =5)
tree_approach4 <- train(target~., data=df_train ,method ="rpart2",trControl =trControl, tuneGrid = tuneGrid)
plot(tree_approach4)
```

```{r}
tree3 <- rpart(target ~.,data = df_train,control=rpart.control(maxdepth=4))
pred <- predict(tree3, df_test, type = "class")
cm2 <- confusionMatrix(data = pred, reference = df_test$target, positive = "long")
cm2$overall[1]
```


