
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 11: Predictive Modeling - Part 2"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2020_assignment11.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install the package `mlbench` and use the follows to import the data

```{r}
library(mlbench)
data(PimaIndiansDiabetes)
df <- PimaIndiansDiabetes
names(df)[9] <- 'target'
df$target <- factor(df$target)
```

- Set seed to be 2020. 
- Partition the data into 80% training and 20% testing.  
```{r}
library(caret)
set.seed(2020)
splitIndex <- createDataPartition(df$target, p = .80, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
```

-------

2. Use cross-validation with 10 k-folds to find the maxdepth with the greatest accuracy. Plot the accuracy associated with different maxdepths against the maxdepths. The range to search for maxdepth is from 1 to 10. 
```{r}
tuneGrid = expand.grid(maxdepth = 1:10)
trControl = trainControl(method ="cv",number =10)
tree_approach2 <- train(target~., data=df_train,method ="rpart2",trControl =trControl, tuneGrid = tuneGrid)
plot(tree_approach2)
print(tree_approach2)
```
-------

3. Make the final decision to select the maxdepth for your decision tree.  Is your selected maxdepth the same as the maxdepth found in 2. 
```{r}
library(rpart)
library(rattle)
tree3 <- rpart(target ~.,data = df_train,control=rpart.control(maxdepth=4))
fancyRpartPlot(tree3)
```


-------

4. Calculate the accuracy of your decision tree (the decision tree with your selected maxdepth in 3) on the test data. 
```{r}
library(e1071)
pred <- predict(tree3, df_test, type = "class")
cm <- confusionMatrix(data = pred, reference = df_test$target, positive = "pos")
cm$overall[1]
```
-------

5. Redo 2-4 with an alternative method to cross-validation. 
```{r}
tuneGrid = expand.grid(maxdepth = 1:10)
trControl = trainControl(method ="LGOCV",number =10)
tree_approach3 <- train(target~., data=df_train,method ="rpart2",trControl =trControl, tuneGrid = tuneGrid)
plot(tree_approach3)
print(tree_approach3)
```

```{r}
tree1 <- rpart(target ~.,data = df_train,control=rpart.control(maxdepth=4))
fancyRpartPlot(tree1)
tree2 <- rpart(target ~.,data = df_train,control=rpart.control(maxdepth=6))
fancyRpartPlot(tree2)
```
```{r}
pred <- predict(tree1, df_test, type = "class")
cm <- confusionMatrix(data = pred, reference = df_test$target, positive = "pos")
cm$overall[1]
pred <- predict(tree2, df_test, type = "class")
cm <- confusionMatrix(data = pred, reference = df_test$target, positive = "pos")
cm$overall[1]
```

