
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 13: Writing a function - Conditional Statement"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2020_assignment13.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Github Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

#### NOTICE: Question 7 and 8 are optional. 

-------

1. Write a function to calculate the age of a person.  Give an example to test your function. 

- Input: a number, x, (year born)

- Output: Print out "You are r age". Where r is the age of the person, i.e. 2020 - x. 

Hint: [Similar Function](https://bryantstats.github.io/math421/gganimate/13_writing_functions.html#29)


```{r}
age_calc <- function(x)
{
  r <- 2020 - x
  print(paste0('You are ', r, ' years old'))
}
```

```{r}
age_calc(1999)
```

-------

2. Write the following function. Give an example to test your function. 

- Input: a number

- Output: print out: "You input an even number!" if the number is event, or "You input an odd number!" otherwise. 

Hint: [Similar Function](https://bryantstats.github.io/math421/gganimate/13_writing_functions.html#33)

```{r}
even_odd <- function(x)
{
  if ((x %% 2) == 0)
  {
    print('Your number is even')
  }
  else
  {
    print("You've input an odd number")
  }
}
```

```{r}
even_odd(7)
```

-------

3. Write the following function.  Give an example to test your function. 

- Input: a numeric vector 

- Output:  

  - if the input vector has missing values: return the input vector with missing values replaced by mean
  
  - if the input vector has no missing value: return the same input vector
  
Hint: [Similar Function](https://bryantstats.github.io/math421/gganimate/13_writing_functions.html#37)

```{r}
mean_replacement <- function(x)
{
  if (is.numeric(x))
  {
    mean_impute <- mean(x, na.rm=T)
    library(tidyverse)
    x <- replace_na(x, mean_impute)
  }
return(x)
}
```

```{r}
mean_replacement(c(1,2,3,4,5,6,7,8,NA,NA))
```


-------

4. Write the following function.  Give an example to test your function. 

- Input: a vector x 

- Output:  The vector x where the missing values replaced by the mean (if x is numeric) or the mode (if x is non-numeric).  If x does not have missing value, return the same vector x.  

Hint: Combine the function in Question 3 and [this function](https://bryantstats.github.io/math421/gganimate/13_writing_functions.html#37)

```{r}
replacement2 <- function(x)
{
   if (is.numeric(x))
  {
    mean_impute <- mean(x, na.rm=T)
    library(tidyverse)
    x <- replace_na(x, mean_impute)
   }
  else
  {
    mode_replace <- names(sort(-table(x)))[1]
    x <- replace_na(x, mode_replace)
  }
return(x)
}
```


```{r}
library(tidyverse)
df <- read_csv('titanic.csv')
replacement2(df$Age)
replacement2(df$Embarked)
```

-------

5. Write the following function. Give examples to test your function. 

- Input: A data frame of two variables x and y

- Output: 

  - A boxplot of x by y if x is numeric and y is non-numeric
 
  - A boxplot of y by x if y is numeric and x is non-numeric
 
  - print out 'This function cannot visualize your data' otherwise

Hint: 

- [Similar Function](https://bryantstats.github.io/math421/gganimate/13_writing_functions.html#41)
 
- You can refer to this slide to plot a boxplot: https://bryantstats.github.io/math421/slides/6_viz.html#36

```{r}
plot_generate <- function(d)
{
  if(is.numeric(d[[1]])|!is.numeric(d[[2]]))
  {
    d %>% ggplot(aes(x = d[[2]], y = d[[1]]))+
      geom_boxplot()+
      labs(x = names(d)[2], fill = names(d)[1])
  }
  else if (!(is.numeric(d[[1]])|is.numeric(d[[2]])))
  {
    d %>% ggplot(aes(x = d[[1]], fill = d[[2]]))+
      geom_boxplot()+
      labs(x = names(d)[1], fill = names(d)[2])
  }
  else 
  {
    print('This function cannot visualize your data.')
  }
}
```


```{r}
d <- df %>% select(Age, Sex)
plot_generate(d)
```
 
-------
 
6. Combine the function in Question 5 and the function in this example ([Link](https://bryantstats.github.io/math421/gganimate/13_writing_functions.html#41)) to have a function that can plot all possible cases (2 categorical, 2 numeric, 1 numeric and 1 categorical). 

```{r}
advanced_plot <- function(d)
{
  if((is.numeric(d[[1]])&is.numeric(d[[2]])))
  {
       d %>% ggplot(aes(x = d[[1]], y = d[[2]]))+
      geom_point(position = 'jitter')+
      labs(x = names(d)[1], y = names(d)[2])
  }
  else if(!is.numeric(d[[1]]) & !is.numeric(d[[2]]))
  {
    d %>% ggplot(aes(x = d[[1]], fill = d[[2]]))+
    geom_bar(position = 'dodge')+
    labs(x = names(d)[1], fill = names(d)[2]) 
  }
  else if(is.numeric(d[[1]])& !is.numeric(d[[2]]))
  {
    d %>% ggplot(aes(x = d[[2]], y = d[[1]]))+
      geom_boxplot()+
      labs(x = names(d)[2], fill = names(d)[1])
  }
  else
  {
    d %>% ggplot(aes(x = d[[1]], fill = d[[2]]))+
      geom_boxplot()+
      labs(x = names(d)[1], fill = names(d)[2])
  }

}
```


```{r}
df$Pclass <- factor(df$Pclass)
d <- df %>% select(Age, Sex)
e <- df %>% select(Age, Fare)
f <- df %>% select(Sex, Pclass)
advanced_plot(d)
advanced_plot(e)
advanced_plot(f)
```

-------

#### NOTICE: Question 7 and 8 are optional. 

-------

7. Write the following function. Give examples to test your function. 

- Input: 

  - input_data: a clean data frame with a variable name `target`. The `target` variable is also binary. 
  
  - train_percent: a number presenting a proportion of training data. The default train_percent is .8

- Output: the accuracy of the decision model `rpart` where the training data is train_percent. 

-------

8. Write the following function. Give examples to test your function. 

- Input: 

  - input_data: a clean data frame with a variable name `target`. The `target` variable is also binary. 
  
  - train_percent: a number presenting a proportion of training data. The default train_percent is .8

- Output: the plot of variable important by random forest trained by caret. 




