
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 14: Writing a function - Loop"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2020_assignment14.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Github Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```
```{r}
mean_replacement <- function(x)
{
  if (is.numeric(x))
  {
    mean_impute <- mean(x, na.rm=T)
    library(tidyverse)
    x <- replace_na(x, mean_impute)
  }
return(x)
}

replacement2 <- function(x)
{
   if (is.numeric(x))
  {
    mean_impute <- mean(x, na.rm=T)
    library(tidyverse)
    x <- replace_na(x, mean_impute)
   }
  else
  {
    mode_replace <- names(sort(-table(x)))[1]
    x <- replace_na(x, mode_replace)
  }
return(x)
}
```

-------

1. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: a data frame with all the missing of numeric variables replaced by the associated means.

Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/14_writing_functions.html#28)

```{r}
imputation <- function(x)
{
  for (i in 1:length(x))
  {
    df[[i]] <- mean_replacement(df[[i]])
  }
  return(df)
}
```

```{r}
library(tidyverse)
df <- read_csv('titanic.csv')
imputation(df)
```

-------

2. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: a data frame with all the missing of variables replaced by the associated means (for numeric variables) or modes (for non-numeric variables).

Hint: Combine the function in Problem 1 and the function in [this example](https://bryantstats.github.io/math421/gganimate/14_writing_functions.html#28)

```{r}
imputation_V2 <- function(x)
{
  for (i in 1:length(x))
  {
    df[[i]] <- replacement2(df[[i]])
  }
 return(df)
}
```

```{r}
imputation_V2(df)
```

-------

3. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: Bar plots of all non-numeric variables

Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/14_writing_functions.html#32)

```{r}
bar_plot <- function(x)
{
  library(ggplot2)
  for (i in 1:length(x))
  {
    if (!is.numeric(df[[i]]))
    {
      print(ggplot(df, aes(x = df[[i]]))+ 
              geom_bar()+
              labs(x = names(df)[i]))
    }
  }
}
```

```{r}
bar_plot(df)
```

-------

4. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: all possible the bar plots of a non-numeric variable filled by a non-numeric variable.

Hint: [Similar function](https://bryantstats.github.io/math421/gganimate/14_writing_functions.html#40)

```{r}
bar_plot2 <- function(x)
{
  l <- length(x)
  for (i in 1:(l-1))
    for (j in (i+1):l)
  {
    if (!is.numeric(df[[i]])&!is.numeric(df[[j]]))
    {
      print(ggplot(df, aes(x = df[[i]], fill = df[[j]]))+ 
              geom_bar()+
              labs(x = names(df)[i], fill = names(df)[j]))
    }
  }
}
```

```{r}
bar_plot2(df)
```

-------

5. Write the following function. Give examples to test your function.

- Input: a data frame

- Output: 

  - all possible the bar plots of a non-numeric variable filled by a non-numeric variable.
  
  - all possible the density plots of a numeric variable colored by a non-numeric variable
  
  - all possible the scatter plots.

Hint: Combine [this function](https://bryantstats.github.io/math421/gganimate/14_writing_functions.html#36), [this function](https://bryantstats.github.io/math421/gganimate/14_writing_functions.html#39), and the function in Question 4. One way to combine is creating a new function, `quick_plot`, and call these three functions within `quic_kplot`. 

```{r}
density_plot <- function(x)
{
  l <- length(x)
  for (i in 1:(l-1))
    for (j in (i+1):l)
  {
    if (is.numeric(df[[i]])&!is.numeric(df[[j]]))
    {
      print(ggplot(df, aes(x = df[[i]], fill = df[[j]]))+ 
              geom_bar()+
              labs(x = names(df)[i], fill = names(df)[j]))
    }
  }
}

scatter_plot <- function(x)
{
  l <- length(x)
  for (i in 1:(l-1))
    for (j in (i+1):l)
  {
    if (is.numeric(df[[i]])&is.numeric(df[[j]]))
    {
      print(ggplot(df, aes(x = df[[i]], y = df[[j]]))+ 
              geom_point()+
              labs(x = names(df)[i], y = names(df)[j]))
    }
  }
}
```

```{r}
quickplot <- function(x)
{
  density_plot(x)
  scatter_plot(x)
  bar_plot(x)
}
```

```{r}
quickplot(df)
```

