
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 9: Visualization - Revealing a graph"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2020_assignment9.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Use the dataset by of covid 19 by WHO at https://covid19.who.int/WHO-COVID-19-global-data.csv. Find the three countries with the most numbers of deaths by Covid-19. 
```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
df <- read_csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')
df$Date_reported <- ymd(df$Date_reported)
df %>% filter(Date_reported == max(df$Date_reported)) %>% arrange(-Cumulative_deaths) %>% head(3)
```

Hint: 

-  Use `filter` to select the most current date 

-  Pipe with `arrange(-Cumulative_deaths)` to rank the data by the number of cumulative deaths


2. Make a plot revealing the number of deaths in the three countries with the most numbers of deaths
```{r}
library(gganimate)
library(gifski)
d1 <- df %>% filter((Country_code == 'US')|(Country_code=='IN')|(Country_code == 'BR'))

ggplot(d1, mapping = aes(x=Date_reported, y=Cumulative_deaths, color=Country_code))+ geom_line()+  transition_reveal(Date_reported)
```

3. Create the new variable (column) `death_per_cases` recording the number of deaths per cases (Hint: divide cumulative deaths by cumulative cases).  What are the three countries with the highest deaths per cases? 
```{r}
df$death_per_cases <- (df$Cumulative_deaths/df$Cumulative_cases)
df %>% filter(Date_reported == max(df$Date_reported)) %>% arrange(-death_per_cases) %>% head(3)
```

4. Make a plot revealing the number of deaths per cases of the US, Italy and Mexico. 
```{r}
d2 <- df %>% filter((Country_code == 'US')|(Country_code=='IT')|(Country_code == 'MX'))

ggplot(d2, mapping = aes(x=Date_reported, y=death_per_cases, color=Country_code))+ geom_line()+  transition_reveal(Date_reported)
```

