
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 12: Predictive Modeling - Part 3"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2020_assignment12.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install the package `mlbench` and use the follows to import the data

```{r}
library(mlbench)
data(PimaIndiansDiabetes)
df <- PimaIndiansDiabetes
names(df)[9] <- 'target'
df$target <- factor(df$target)
```

- Set seed to be 2020. 
- Partition the data into 80% training and 20% testing.  
```{r}
library(caret)
set.seed(2020)
splitIndex <- createDataPartition(df$target, p = .80, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
```

-------

2. Use cross-validation of 30 folds to tune random forest (method='rf').  What is the `mtry` value that produces the greatest accuracy?
```{r}
tuneGrid = expand.grid(mtry = 2:8)
trControl = trainControl(method ="cv",number =30)
tree_approach1 <-train(target~.,method ="rf",trControl =trControl,data=df_train, tuneGrid = tuneGrid) 
plot(tree_approach1)
print(tree_approach1)
```
 
-------

3. Use cross-validation with of 30 folds to tune random forest (method='ranger').  What are the parameters that produce the greatest accuracy?
```{r}
library(ranger)
tuneGrid = expand.grid(mtry =2:8,splitrule = c('gini', 'extratrees'), min.node.size = c(1:5))
trControl = trainControl(method ="cv",number =30)
tree_approach2 <-train(target~., data=df_train,method="ranger",trControl =trControl,tuneGrid = tuneGrid)
plot(tree_approach2)
print(tree_approach2)
```

-------

4. Go to https://topepo.github.io/caret/available-models.html and pick a classification model.  Tune the classification model using cross-validation of 30 folds. 
```{r}
tuneGrid = expand.grid(nIter =2:10, method='cv')
trControl = trainControl(method ="cv", number = 30)
tree_approach3 <-train(target~., data=df_train,method="adaboost",trControl =trControl, tuneGrid = tuneGrid)
plot(tree_approach3)
print(tree_approach3)
```

5. Compare the three models in question 2, 3, and 4 to select the final model.  Evaluate the accuracy of the final model on the test data. 
```{r}
pred <- predict(tree_approach1, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$target, positive = "pos")
cm$overall[1]
pred <- predict(tree_approach2, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$target, positive = "pos")
cm$overall[1]
pred <- predict(tree_approach3, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$target, positive = "pos")
cm$overall[1]
```

