---
title: "Midterm Presentation"
author: "Dan Barrett"
date: "10/21/2020"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

```{r}
library(tidyverse)
library(ggplot2)
library(gganimate)
library(gifski)
library(rattle)
library(e1071)
library(rpart)
library(caret)
df = read_csv('midterm.csv')
```


## Plot 1
```{r, fig.height= 4, fig.width=6}
df %>% ggplot() + geom_point(mapping=aes(x = age, y = los), na.rm = TRUE) + ggtitle("Length of Stay by Age scatterplot") + labs(y= 'Length of Stay in days', x = 'Age in Years')
```

## Plot 2
```{r, fig.height= 4, fig.width=6}
df %>% ggplot() + geom_smooth(mapping=aes(x=age, y =los), na.rm = TRUE)+ ggtitle("Average Length of Stay by Age") + labs(y= 'Length of Stay in days', x = 'Age in Years')
```


## Plot 3
```{r, fig.height= 4, fig.width=6}
df %>% ggplot() + geom_point(mapping=aes(x = age, y = tot), na.rm = TRUE)+ ggtitle("Cost of Stay by Age scatterplot") + labs(y= 'Cost of Stay in dollars', x = 'Age in Years')
```

## Plot 4
```{r, fig.height= 4, fig.width=6}
df %>% ggplot() + geom_smooth(mapping=aes(x = age, y = tot), na.rm = TRUE)+ ggtitle("Average Cost of Stay by Age") + labs(y= 'Cost of Stay in dollars', x = 'Age in Years')
```



## Plot 5
```{r, fig.height= 4, fig.width=6}
df %>% ggplot() + geom_bar(mapping=aes(x = raceethn, fill= raceethn), na.rm = TRUE)+ ggtitle("Number of Patients by Race") + labs(y= 'Number of Patients', x = 'Race as Coded')
```


## Plot 6
```{r, fig.height= 4, fig.width=6}
df %>% ggplot() + geom_bar(mapping=aes(x = provider), na.rm = TRUE)+ ggtitle("Number of Patients by Provider") + labs(y= 'Number of Patients', x = 'Provider Codes')
```


## Plot 7
```{r, fig.height= 4, fig.width=6}
df %>% ggplot() + geom_bar(mapping=aes(x = payer), na.rm = TRUE)+ ggtitle("Number of Patients by Payment Type") + labs(y= 'Number of Patients', x = 'Payment Type Codes')
```

## Plot 8
```{r, fig.height= 4, fig.width=6}
df %>% ggplot() + geom_bar(mapping=aes(x = provider, fill = payer), na.rm = TRUE)+ ggtitle("Number of Patients by Race") + labs(y= 'Number of Patients', x = 'Race as Coded')
```


## Plot 9
```{r, fig.height= 4, fig.width=6}
df %>% ggplot() + geom_smooth(mapping=aes(x = moa , y = tot), na.rm = TRUE)+ ggtitle("Average Cost of Stay by Month of Admission") + labs(y= 'Average Cost of Stay in dollars', x = 'Month of Admission')
```




## Plot 10
```{r, fig.height= 4, fig.width=6}
df %>% group_by(payer) %>% summarise(mean_los = mean(los)) %>% ggplot() + geom_col(mapping=aes(x = payer, y = mean_los), na.rm = TRUE)+ ggtitle("Average Length of Patient Stay by Payment Type") + labs(y= 'Average Length of Stay in days', x = 'Patient Payment Type Code')
```


## Plot 11 / Animation
```{r, fig.height= 4, fig.width=5}
df$provider <- factor(df$provider)
df1 <- df %>% group_by(moa, provider) %>% summarise(mean_cost = mean(tot))
ggplot(df1, mapping = aes(x = moa, y = mean_cost, color = provider)) + transition_reveal(moa) + geom_line() + ggtitle("Average Cost by Provider Over the Year") + labs(y= 'Average Cost of Stay in dollars', x = 'Month of Admission') + geom_text(aes(label = provider))
```



```{r}
mysample <- df[sample(1:nrow(df), 2000,
   replace=FALSE),]
median_tot <- df %>% summarise(median = median(tot))
mysample$target <- case_when(
  mysample$tot <= 21854 ~ "low",
  TRUE ~ "high"
)
df = subset(mysample, select = c(age, sex, raceethn, provider, moa, mod, admtype, campus, los, target))
df$target <- factor(df$target)
df$sex <- factor(df$sex)
df$raceethn <- factor(df$raceethn)
df$provider <- factor(df$provider)
df$admtype <- factor(df$admtype)
df$campus <- factor(df$campus)
df <- df %>% na.omit((df$raceethn) | (df$admtype))
splitIndex <- createDataPartition(df$target, p = .90, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
tuneGrid = expand.grid(maxdepth = 1:10)
trControl = trainControl(method ="cv",number =5)
tree_approach1 <- train(target~., data=df_train ,method ="rpart2",trControl =trControl, tuneGrid = tuneGrid)
tuneGrid = expand.grid(nIter =2:10, method='cv')
trControl = trainControl(method ="cv",number =5)
tree_approach2 <- train(target~., data=df_train ,method ="adaboost",trControl =trControl, tuneGrid = tuneGrid)
tuneGrid = expand.grid(mtry = 2:5)
trControl = trainControl(method ="cv",number =5)
tree_approach3 <- train(target~., data=df_train ,method ="rf",trControl =trControl, tuneGrid = tuneGrid)
model_accuracy <- resamples(list(adaboost = tree_approach2,
                                 forest = tree_approach3,
                                 tree = tree_approach1))
```




## Comparing Accuracy
-Random Forest performs the best 

```{r}
bwplot(model_accuracy)
```



## Best Model
```{r, fig.height= 4, fig.width=6}
tree1 <- rpart(target ~.,data = df_train,control=rpart.control(maxdepth=5))
fancyRpartPlot(tree1)
pred <- predict(tree_approach1, df_test, type = "raw")
cm <- confusionMatrix(data = pred, reference = df_test$target, positive = "high")
cm$overall[1]
```




## Predicting Length of Stay
```{r}
df <- read_csv('midterm.csv')
df <- df[sample(1:nrow(df), 2000,
   replace=FALSE),]
median_los <- df %>% summarise(median = median(los))
df$target <- case_when(
  df$los <= 4 ~ "short",
  TRUE ~ "long"
)
df = subset(df, select = c(age, sex, raceethn, provider, moa, mod, admtype, campus, tot, target))
df$target <- factor(df$target)
df$sex <- factor(df$sex)
df$raceethn <- factor(df$raceethn)
df$provider <- factor(df$provider)
df$admtype <- factor(df$admtype)
df$campus <- factor(df$campus)
df <- df %>% na.omit((df$raceethn) | (df$admtype))
splitIndex <- createDataPartition(df$target, p = .90, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
tuneGrid = expand.grid(maxdepth = 1:10)
trControl = trainControl(method ="cv",number =5)
tree_approach4 <- train(target~., data=df_train ,method ="rpart2",trControl =trControl, tuneGrid = tuneGrid)
```




## Model Predicting Lenght of Stay
```{r}
tree3 <- rpart(target ~.,data = df_train,control=rpart.control(maxdepth=4))
pred <- predict(tree3, df_test, type = "class")
cm2 <- confusionMatrix(data = pred, reference = df_test$target, positive = "long")
fancyRpartPlot(tree3)
cm2$overall[1]
```


